A Fully Decentralized Infrastructure for Automated and Trusted IoT Data Trading

### 2020-06-14 paper.tex
Minor tweaks

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. The real-time data exchangements among devices forms a publish/subscribe relationship of streaming data that increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure, in order to address the technical challenges. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

@@

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service. The subscription-based models (e.g. software-as-a-service (SaaS) and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. \cite{SaaS} pointed out that the strength of the relationships between consumers and providers depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

>>>>

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy with other machines, which devices can share and trade their resources. The real-time data exchangements among devices forms a publish/subscribe (pub/sub) relationship of streaming data which devices can transform the data exchangement into subscription-based services. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automatic subscription procedures is also required. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct an IoT-enabled, decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

@@

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service. The subscription-based models (e.g. software-as-a-service (SaaS) and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. \cite{SaaS} pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.
